---
title: "Lab 9"
author: "Kizitor Chukwuma"
date: "10/21/2019"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1
```{r}
getwd()
```

# Task 2

Line A takes a sample 'iter' times with replacement using the 'x' sample.

Line B is the confidence interval for the resampled vector.

Resampling is done with replacement because the original sample is already representative of the population.

## Set 1

```{r}
set.seed(35)
sam=round(rnorm(20,mean=10,sd=4),2)
unique(sample(sam,20,replace=TRUE))
unique(sample(sam,20,replace=TRUE))
unique(sample(sam,20,replace=TRUE))
unique(sample(sam,20,replace=TRUE))
unique(sample(sam,20,replace=TRUE))
```

These samples contain the same amount values of the original sample with no repeated values.

## Set 2

```{r}
unique(sample(sam,20,replace=FALSE))
unique(sample(sam,20,replace=FALSE))
unique(sample(sam,20,replace=FALSE))
unique(sample(sam,20,replace=FALSE))
unique(sample(sam,20,replace=FALSE))
```

These samples contain 20 values and they are all unique.

```{r}
#sample(sam,21,replace=FALSE) #This is impossible without replacement since its trying to have a sample bigger than the population.
```

# Task 3
```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

# Some output to use if necessary
}
```

## a.
```{r}
set.seed(39) 
sam=rnorm(25,mean=25,sd=10)
myboot2(x= sam)
```

## b.
```{r}
set.seed(30) 
sam=rchisq(20,df=3)
myboot2(x= sam)
```

## c.
```{r}
set.seed(40)
sam=rgamma(30,shape=2,scale=3)
myboot2(x= sam)
```

## d.
```{r}
set.seed(10)
sam=rbeta(20,shape1=3,shape2=4)
myboot2(x= sam)
```

